%-------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tikz}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.2in}

% \usepackage[bottom=0.4in,top=0.4in,left=0.5in,right=0.5in]{geometry}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2}\vspace{1pt}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Saifullah Talukder} \\ \vspace{5pt}
    \small \faPhone* \texttt{(880)1914-550383} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{\href{mailto:saifullah.cse16.buet@gmail.com}{saifullah.csebuet@gmail.com}} \hspace{1pt} $|$ 
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Dhaka, Bangladesh}
    \\ \vspace{5pt}
    \hspace{1pt} \faLinkedin \hspace{2pt} \href{https://www.linkedin.com/in/saifullah-talukder}{\textcolor{blue}{linkedin.com/in/saifullah-talukder}} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{2pt} \href{https://github.com/saifullah-talukder}{\textcolor{blue}{github.com/saifullah-talukder}} \hspace{1pt} %$|$
    % \hspace{1pt} \faGlobe \hspace{2pt} \href{https://rathijitpaul.com/}{\textcolor{blue}{rathijitpaul.com}} \hspace{1pt}
    \\ \vspace{-5pt}
\end{center}

%-----------INTROUCTION-----------
\section{ABOUT ME}
 \begin{itemize}[leftmargin=0in, label={}]
    \resumeItem {Hello! I'm Saifullah Talukder, currently thriving as a Software Engineer at {\textcolor{blue}{\href{https://bangladesh.ai/}{Intelligent Machines Limited}}} with a keen focus on frontend development. Over the past two years, I've honed my skills in crafting comprehensive web applications, transforming wireframes into fully-functional, quality websites under tight deadlines. I'm now eager to embrace a more challenging role in frontend or full-stack development, where I can further expand my expertise and contribute effectively.}
    
 \end{itemize}

%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}: \hspace{41pt} {JavaScript, TypeScript, HTML, CSS}\vspace{2pt} \\
     \textbf{Frameworks \& Tools}: \hspace{1pt} {React, Next.js, Material UI, Tailwind CSS}\vspace{2pt} \\
    }}
 \end{itemize}

%-----------PORTFOLIO-----------
\section{PORTFOLIO}
    \begin{itemize}[leftmargin=0in, label={}]
        \resumeItem{(Note: Project names are codenamed for confidentiality.)}
    \end{itemize}

    \textit{\textbf{Common Features Across Projects}}
    \resumeItemListStart
        \resumeItem {Developed the frontend of various dashboard applications from scratch, adhering to Figma designs using \textbf{React} and \textbf{Next.js}.}
        \resumeItem {Ensured functionality including but not limited to project management, user management, file uploads/downloads, notification service and responsive dashboards.}
        \resumeItem {Built a backend application to work as a proxy between frontend application and multiple other backend services using \textbf{Next.js}.}
        \resumeItem {Built most of the UI from scratch using HTML and CSS. For writing CSS I used \textbf{TailwindCSS}. For some components that are difficult to built like dialog, menu, drawer I used \textbf{Material UI or Headless UI} component library.}
        \resumeItem{Collaborated closely with UX designers, business analysts, and clients to translate business needs into software solutions.}
        \resumeItem{Authored Dockerfiles for seamless deployment by the DevOps team.}
        
    \resumeItemListEnd
    
    \textit{\textbf{Padma Project}}
    \resumeItemListStart
        \resumeItem {It was initially built using plain \textbf{React}. But in order to cater to certain needs of the client it was later migrated to \textbf{Next.js}.}
        \resumeItem{Built APIs using \textbf{Next.js} to work as an intermediary for backend services and file hosting server since they are not exposed to the open internet for security purposes.}
        \resumeItem{Employed Redux Toolkit for state management and introduced a pagination feature for lists.}
    \resumeItemListEnd

    \textit{\textbf{Meghna and Jamuna}}
    \resumeItemListStart
        \resumeItem {As these two projects are quiet similar I developed them using \textbf{Next.js} with a focus on similar features and development cycles.}
        \resumeItem {Utilized Zustand for state management and React Query for API calls.}
    \resumeItemListEnd

    \textit{\textbf{Karnaphuli}}
    \resumeItemListStart
        \resumeItem {This project also is being built using \textbf{Next.js}. I am currently working on it.}
        \resumeItem {Developed data visualization features like bar and doughnut charts.}
    \resumeItemListEnd


%-----------FINAL THOUGHTS-----------
\section{FINAL THOUGHTS}
 \begin{itemize}[leftmargin=0in, label={}]
    \resumeItem {As a passionate software developer, I am committed to continuous learning and improvement. In each project, I strive to combine creativity with technical proficiency, ensuring that every application is not only functional but also user-friendly and aesthetically pleasing. I look forward to the opportunity to bring my skills and dedication to a dynamic and innovative team.}
    
 \end{itemize}

  

\vspace{-8pt}

\end{document}
